\cleardoublepage
%\pagebreak
\phantomsection
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}

\bibitem{vandrunen}VanDrunen, T. J. 2004. Partial redundancy elimination for global value numbering (Doctoral dissertation, Purdue University).

\bibitem{kildall}Gary A. Kildall. 1973. A unified approach to global program optimization. In \emph{Proceedings of the 1st annual ACM SIGACT-SIGPLAN symposium on Principles of programming languages} (POPL '73). ACM, 194-206.\ \url{http://doi.acm.org/10.1145/512927.512945}

\bibitem{awz}B. Alpern, M. N. Wegman, and F. K. Zadeck. 1988. Detecting equality of variables in programs. In \emph{Proceedings of the 15th ACM SIGPLAN-SIGACT symposium on Principles of programming languages} (POPL '88). ACM, 1-11.\ \url{http://doi.acm.org/10.1145/73560.73561}

\bibitem{ruthing}R\"uthing, O., Knoop, J., \& Steffen, B. 1999. Detecting equalities of variables: Combining efficiency with precision. \emph{Static Analysis}, 848-848.

\bibitem{gargi}Karthik Gargi. 2002. A sparse algorithm for predicated global value numbering. In \emph{Proceedings of the ACM SIGPLAN 2002 Conference on Programming language design and implementation} (PLDI '02). ACM, 45-56.\ \url{http://doi.acm.org/10.1145/512529.512536}

\bibitem{gulwani}Gulwani, S., \& Necula, G. 2004. A polynomial-time algorithm for global value numbering. \emph{Static Analysis}, 703-1020.

\bibitem{sagvn}Saleena Nabeezath, Vineeth Paleri. 2013. A Simple Algorithm for Global Value Numbering. \emph{arXiv:1303.1880} -\ \url{http://arxiv.org/abs/1303.1880}

\bibitem{suif}The SUIF2 Compiler System -\ \url{http://suif.stanford.edu/suif/suif2/}
\bibitem{gcc}GCC, the GNU Compiler Collection -\ \url{http://gcc.gnu.org/}
\bibitem{llvm}The LLVM Compiler Infrastructure Project -\ \url{http://llvm.org/}
\bibitem{clang}Clang vs Other Open Source Compilers - Clang vs GCC -\ \url{http://clang.llvm.org/comparison.html#gcc}
\bibitem{gcc-structure}Structure of GCC -\ \url{http://gcc.gnu.org/wiki/StructureOfGCC}

\bibitem{dnovillo}Compiler Pipeline, GCC Internals Course - November 2007 -\ \url{http://www.airs.com/dnovillo/200711-GCC-Internals/}

\bibitem{generic}GENERIC -\ \url{http://gcc.gnu.org/onlinedocs/gccint/GENERIC.html}
\bibitem{gimple}GIMPLE -\ \url{http://gcc.gnu.org/onlinedocs/gccint/GIMPLE.html}
\bibitem{rtl}RTL Representation -\ \url{http://gcc.gnu.org/onlinedocs/gccint/RTL.html}

\bibitem{grc}Essential Abstractions in GCC '12 - A workshop on GCC Internals by GCC Resource Center, IIT Bombay.\ \url{http://www.cse.iitb.ac.in/grc/gcc-workshop-12}

\bibitem{gccint}GCC Internals Documentation (for GCC 4.6.3) -\ \url{http://gcc.gnu.org/onlinedocs/gcc-4.6.3/gccint/}

\bibitem{kandr}The C Programming Language, Second Edition by Kernighan \& Ritchie -\ \url{http://cm.bell-labs.com/cm/cs/cbook/}

\bibitem{gcc-ml}The gcc mailing list archives -\ \url{http://gcc.gnu.org/ml/gcc/}
\bibitem{gcc-irc}GCConIRC -\ \url{http://gcc.gnu.org/wiki/GCConIRC}

\end{thebibliography}
