\cleardoublepage
%\pagebreak
\phantomsection
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}

	\bibitem{vandrunen}VanDrunen, T. J. 2004. Partial redundancy elimination for global value numbering (Doctoral dissertation, Purdue University).\ \url{http://docs.lib.purdue.edu/dissertations/AAI3154748/}
\bibitem{kildall}Gary A. Kildall. 1973. A unified approach to global program optimization. In \emph{Proceedings of the 1st annual ACM SIGACT-SIGPLAN symposium on Principles of programming languages} (POPL '73). ACM, 194-206.\ \url{http://doi.acm.org/10.1145/512927.512945}
\bibitem{awz}B. Alpern, M. N. Wegman, and F. K. Zadeck. 1988. Detecting equality of variables in programs. In \emph{Proceedings of the 15th ACM SIGPLAN-SIGACT symposium on Principles of programming languages} (POPL '88). ACM, 1-11.\ \url{http://doi.acm.org/10.1145/73560.73561}
\bibitem{ruthing}R\"uthing, O., Knoop, J., \& Steffen, B. 1999. Detecting equalities of variables: Combining efficiency with precision. \emph{Static Analysis}, 848-848.\ \url{http://dl.acm.org/citation.cfm?id=718137}
\bibitem{gargi}Karthik Gargi. 2002. A sparse algorithm for predicated global value numbering. In \emph{Proceedings of the ACM SIGPLAN 2002 Conference on Programming language design and implementation} (PLDI '02). ACM, 45-56.\ \url{http://doi.acm.org/10.1145/512529.512536}
\bibitem{gulwani}Gulwani, S., \& Necula, G. 2004. A polynomial-time algorithm for global value numbering. \emph{Static Analysis}, 703-1020.\ \url{http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.84.7271}
\bibitem{gcc}GCC, the GNU Compiler Collection -\ \url{http://gcc.gnu.org/}
\bibitem{generic}GENERIC -\ \url{http://gcc.gnu.org/onlinedocs/gccint/GENERIC.html}
\bibitem{gimple}GIMPLE -\ \url{http://gcc.gnu.org/onlinedocs/gccint/GIMPLE.html}
\bibitem{rtl}RTL Representation -\ \url{http://gcc.gnu.org/onlinedocs/gccint/RTL.html}
\bibitem{simple-gvn}Saleena Nabeezath, Vineeth Paleri. 2013. A Simple Algorithm for Global Value Numbering. \emph{arXiv:1303.1880} -\ \url{http://arxiv.org/abs/1303.1880}
\bibitem{scc-vn}Simpson, Loren Taylor. 1996. Value-driven redundancy elimination. Diss. Rice University.\ \url{http://scholarship.rice.edu/handle/1911/16942}
\bibitem{gvn-pre}GVN-PRE -\ \url{http://gcc.gnu.org/wiki/GVN-PRE}
\bibitem{spec-cpu06}SPEC CPU2006 -\ \url{http://www.spec.org/cpu2006/}
\bibitem{gccint}GCC Internals Documentation (for GCC 4.6.3) -\ \url{http://gcc.gnu.org/onlinedocs/gcc-4.6.3/gccint/}
\bibitem{internals-course}GCC Internals Course - November 2007 -\ \url{http://www.airs.com/dnovillo/200711-GCC-Internals/}

\end{thebibliography}
